Sketch Recognition and Understanding

### 2009-08-04 draft/SketchMaster.tex

% During the editing process you will not want to view and print the
% whole document. Uncomment the command below so that only the
% chapters that you want to work on are visible.
%\includeonly{ChapterIntroduction}
%\documentstyle[11pt,unhthesis]{report}
\documentclass[11pt,doublespace]{Sketchthesis}

@@

\usepackage {graphicx}
\usepackage{subfigure}
\usepackage{longtable}
\usepackage{array}
%\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}

@@

\begin{document}
                                                        % TITLE PAGE
                                                        %======================
\title{Sketch Recognition and Understanding}             % My theses title  using Particle Swarm Optimization Algorithm
\author{Maha Mohammed Nabeel El Meseery}                               % Y name
\prevdegrees{B.S.,Computer  Engineering}       		% Your old degree
\major{Computer Engineering}                            % My current major
\degree{Master of Science}                              % My new degree
\degreemonth{}                                      % When awarded. to be added when known
\degreeyear{}                                      %
%th today or first day of writing  December 26 2005 
%\thesisdate[]                                     % Date of document.
\DOCUMENTtype{Thesis}                                   % or DISSERTATION
\Documenttype{Thesis}                                   % or Dissertation
\documenttype{Thesis}                                   % or dissertation
\maketitle

\providecommand{\tabularnewline}{\\}
                                                        % COPYRIGHT PAGE
                                                        %======================
%\copyrightyear{2009}                                    % Delete these
%\makecopyright                                          % if no copyright
                                                    % APPROVAL                                                         %======================
%\thispagestyle{empty}               % Don't do headers or footers.
%\newpage                                                             
%\begin{center}     
%\LARGE  
%\textbf{Sketch Recognition using Particle Swarm Optimization Algorithm}\\
%\normalsize by      \\ 
%\Large  \textbf{ Maha mohamed Nabeel El Meseery}\\
%\vspace*{0.4in}        
%\normalsize
%A Thesis Submitted To the\\
%Faculty of Engineering, Cairo University\\
%in Partial Fulfillment of the\\
%Requirements for the Degree of\\
%MASTER OF SCIENCE
%in\\
%COMPUTER ENGINEERING\\
%
%\end{center}
%          
%    Approved by\\                                           
%Examining Committee:\\
% \makebox[6in]{\hrulefill}\\ 
%Professor Nevin Darwish, Thesis Main Advisor\\
% \makebox[6in]{\hrulefill}\\ 
%Professor Samia Mashali,Thesis Advisor \\
% \makebox[6in]{\hrulefill}\\  
%Assoc. Professor Magda Fayek,Thesis Advisor\\ 
% \makebox[6in]{\hrulefill}\\ 
%Professor  Ashraf Abd El Wahab, Member\\
% \makebox[6in]{\hrulefill}\\ 
%Professor Mohamed Zaki Abd ElMegeed, Member\\
% \makebox[6in]{\hrulefill}\\ 
  % \\   you need...\\
%\makeapproval                                           %

>>>>

% During the editing process you will not want to view and print the
% whole document. Uncomment the command below so that only the
% chapters that you want to work on are visible.
%\includeonly{ChapterIntroduction}
%\documentstyle[11pt,unhthesis]{report}
\documentclass[11pt,doublespace]{SketchThesis}

@@

\usepackage {graphicx}
\usepackage{subfigure}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{array}
%\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}

@@

\begin{document}
                                                        % TITLE PAGE
                                                        %======================
\title{Sketch Recognition and Understanding}             % My theses title  using Particle Swarm Optimization Algorithm
\author{Maha Mohammed Nabeel El Meseery}                               % Y name
\prevdegrees{B.S.,Computer  Engineering}       		% Your old degree
\major{Computer Engineering}                            % My current major
\degree{Master of Science}                              % My new degree
\degreemonth{}                                      % When awarded. to be added when known
\degreeyear{}                                      %
\superad{Professor Nevin Darwish\\Professor Samia Mashali\\Assoc. Professor Magda Fayek\\}
%th today or first day of writing  December 26 2005 
%\thesisdate[]                                     % Date of document.
\DOCUMENTtype{Thesis}                                   % or DISSERTATION
\Documenttype{Thesis}                                   % or Dissertation
\documenttype{Thesis}                                   % or dissertation

\maketitle

                                                        % COPYRIGHT PAGE
                                                        %======================
%\copyrightyear{2009}                                    % Delete these
%\makecopyright                                          % if no copyright
                                                    % APPROVAL                                                         %======================
\thispagestyle{empty}               % Don't do headers or footers.
\newpage                                                             
\begin{center}     
\LARGE  
\textbf{Sketch Recognition and Understanding}\\
\normalsize by      \\ 
\Large  \textbf{ Maha Mohamed Nabeel El Meseery}\\
\vspace*{0.4in}        
\normalsize
A Thesis Submitted To the\\
Faculty of Engineering, Cairo University\\
in Partial Fulfillment of the\\
Requirements for the Degree of\\
MASTER OF SCIENCE
in\\
COMPUTER ENGINEERING\\

\end{center}

    Approved by\\                                           
Examining Committee:\\
 \makebox[6in]{\hrulefill}\\ 
Professor Nevin Darwish, Thesis Main Advisor\\
 \makebox[6in]{\hrulefill}\\ 
Professor Samia Mashali,Thesis Advisor \\
 \makebox[6in]{\hrulefill}\\  
Assoc. Professor Magda Fayek,Thesis Advisor\\ 
 \makebox[6in]{\hrulefill}\\ 
Professor  Ashraf Abd El Wahab, Member\\
 \makebox[6in]{\hrulefill}\\ 
Professor Mohamed Zaki Abd ElMegeed, Member\\
 \makebox[6in]{\hrulefill}\\ 
  % \\   you need...\\
%\makeapproval                                           %
